Lucy.js: Client-Side Indexes for Fast Full-Text Searching

### 2014-12-11 paper/paper.tex
bugs
final paper

Every node can also potentially include a list of document ids, for documents that contain its prefix as a token (i.e. not a prefix of some longer token). Nodes without children must contain a list of document ids, but internal nodes can also contain document ids. For example, the node for “cat” would contain document ids of documents with the word "cat" itself, as well as children, for terms like "catsitting", "caturday" or "catnip". For these examples, the list of children could be \texttt{['n', 's', 'u']}.

@@

\subsubsection{Leaf and path Shrink}

@@

The data also shows that the number of results has an  impact on lookup time. The three graphs are tiered such that "feel", with the most results, is also the slowest query. While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.

>>>>

Every node can also potentially include a list of document ids, for documents that contain its prefix as a token (i.e. not a prefix of some longer token). Nodes without children must contain a list of document ids, but internal nodes can also contain document ids. For example, the node for ``cat” would contain document ids of documents with the word ``cat" itself, as well as children, for terms like ``catsitting", ``caturday" or ``catnip". For these examples, the list of children could be \texttt{['n', 's', 'u']}.

@@

\subsubsection{Leaf and Path Shrink}

@@

The data also shows that the number of results has an  impact on lookup time. The three graphs are tiered such that ``feel", with the most results, is also the slowest query. While the lookup logic is parallelized so that the text for multiple matching document ids can be retrieved concurrently, the number of lookups that are done to retrieve this text has an impact on performance.
